Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-11 tex/VHzQ.tex
Modifications to variability section

Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e. W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$. 
H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
4.13$\mu$m at $z=7.50$. 
%%
Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 27 WFCAM and 16 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter. 4 objects are in common to both, so this sample of 39 is our starting point for variability investigations. The four objects in common are: CFHQS J0216-4555; SDSS J0959+0227; SDSS J1000+0234; VIK J1148+0056. 
%% is SDSSJ0958+3524 special at all??

>>>>

Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$. 
H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
4.13$\mu$m at $z=7.50$. 
%%
Less well understood is the temporal behaviour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux. 1 objects is in common to both, so this sample of 32 is our starting point for variability investigations. The common object is VIK J1148+0056. 
%% is SDSSJ0958+3524 special at all??
